---
title: Bar Graph= The Best Kind of Graph
author: 'Maria Williams '
date: '2017-10-08'
slug: bar-graph-the-best-kind-of-graph
categories:
  - R Studio
tags:
  - ggplot2
  - Bargraph
---
I am sure all of you know what a bar graph is, well today we are going to code for one. We are going to take baseball teams in 1980 and order them by homeruns. Let's begin. The first thing we must do is bring down our databases with library.
```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```
Great! Now let's gather our information.We are going to want to gather teams and the homeruns from 1980. The code is as follows:
```{r}
query<-"SELECT name,HR
From Teams
WHERE yearID=1980
ORDER BY HR"
sqldf(query)

``` 
Let's store that information into result to make it a little bit easier to handle. We also want to save it as a factor so it will order our results in descending order.
```{r}
query<-"SELECT name,HR
From Teams
WHERE yearID=1980
ORDER BY HR"
result<-sqldf(query)
result$name<-factor(result$name,levels=result$name)
```
Great! Let's make our graph! Like the histogram, we can control the fill and the border outline of the bars! I made mine purple and blue!
```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity',color='blue',fill='purple')+
  coord_flip()+
  ylab('homeruns')+
  xlab("team")+
  ggtitle('1980 Team Homerun Distribution')


```

