---
title: Oh the Joy of Time Series Plots
author: 'Maria Williams '
date: '2017-09-28'
slug: oh-the-joy-of-time-series-plots
categories:
  - R Studio
tags:
  - ggplot2
  - timeseriesplot
---

homeruns. We are going to visualize that data through a time series plot.The first thing we must do is bring down all our databases through library.
```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```
Great, now that we have our databases loaded, we can gather the information needed.The coding for the information is as follows:
```{r}
query<-"SELECT yearID,HR
FROM Batting
WHERE playerID='ruthba01'"
sqldf(query)
```
Awesome, now that we have the information, let's store that into result.
```{r}
query<-"SELECT yearID,HR
FROM Batting
WHERE playerID='ruthba01'"
result<-sqldf(query)
```
Great! Now let's make the graph! The coding for the graph is as follows:
```{r}
ggplot()+
  geom_line(data=result,aes(x=yearID,y=HR))+
  geom_point(data=result,aes(x=yearID,y=HR))+
  ggtitle("Ruth's Homerun Totals Through the Years")+
  xlab("year")+
  ylab("homerun")
```
Wow, that looks great!
