---
title: Scatterplots!
author: 'Maria Williams '
date: '2017-09-28'
slug: scatterplots
categories:
  - R Studio
tags:
  - scatterplot
  - ggplot2
---

Today we will learn how to visualize our data using scatter plots. The first thing we need to do is tell R studio where we are getting our data from. We need to bring in the Lahman Baseball database, SQLDF, and ggplot2 with library. 
```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

After these databases are brought in, we are going to look for some baseball player's career homeruns and strikeouts. The one caught is that they need to have more than 400 homeruns.The coding is as follows:
```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400
"
sqldf(query)
```
Yay! We have gathered all of the data needed to make this scatter plot!To make or lives easier, let's clean up the information and save it as result.
```{r}
query<- "SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```
Great! Now let's make our scatterplot!
```{r}
ggplot()+
  geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3,color="blue")+
  ggtitle("Career Strikeouts VS Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```
Beautiful! Now let's move on to the next graph.
